### 2017-05-31 doc/categories.tex
Plots.

%-----------------
\label{subsec:omission-text-vis}
\begin{figure*}[t]
%\hspace*{-0.3in}
\setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.6]{imaginet-omission-pos-boxplot.png} &
  \includegraphics[scale=0.6]{imaginet-omission-dep-boxplot.png} \\
  \end{tabular}

\caption{Distribution of omission scores for POS (left) and dependency labels
  (right), for the {\sc Textual} and {\sc Visual} pathways and for
  {\sc LM}. Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet}
\end{figure*}

\begin{figure*}[t]
  \centering
  \hspace*{-0.2in}
  \setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.55]{imaginet-omission-ratio-pos-boxplot.png} &
  \includegraphics[scale=0.55]{imaginet-omission-ratio-dep-boxplot.png} \\  
  \end{tabular}
  \caption{Distributions of log ratios of omission scores of {\sc Textual} to {\sc Visual} per
    POS (left) and dependency labels (right). Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet-ratio}
\end{figure*}

@@

Figure~\ref{fig:omission-imaginet-ratio} compares the two pathways of
{\sc Imaginet} directly using the log of the ratio of the {\sc Visual}
to {\sc Textual} omission scores, and plots the distribution of this
ratio for different POS and dependency labels.  Log ratios above zero
indicate stronger association with the {\sc Visual} pathway and below
zero with the {\sc Textual} pathway. We see that in relative terms,
{\sc Visual} is more sensitive to adjectives (JJ), nouns (NNS, NN) and
numerals (CD), and {\sc Textual} to the prepositions (TO, IN),
determiners (DT, WDT) and pronouns (PRP) as well as some types of
verbs (VBZ, VBP).

This picture is complemented by the analysis of the
relative importance of dependency relations: {\sc Visual} pays most
attention to the relations {\sc nsubjpass, attr, amod, nsubj, root,
  compound, dobj, nummod}
whereas {\sc Textual} is more sensitive to {\sc det, mark, prep, aux,
  auxpass, cc, poss, advmod, prt, relcl}.
As expected, {\sc Visual} is more focused on grammatical
functions typically filled by semantically contentful words, while
{\sc Textual} distributes its attention more uniformly and 
attends relatively more to purely grammatical functions.

@@

\begin{figure*}[t]
  \centering
  \hspace*{-0.2in}
  \setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.55]{imaginet-omission-quotient-pos-boxplot.png} &
  \includegraphics[scale=0.55]{imaginet-omission-quotient-dep-boxplot.png} \\  
  \end{tabular}
  \caption{Distributions of log ratios of omission scores of {\sc LM} to {\sc Textual} per
    POS (left) and dependency labels (right). Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet-quotient}
\end{figure*}

>>>>

%-----------------
\label{subsec:omission-text-vis}
\begin{figure}[!htbp]
\centering
%\hspace*{-0.3in}
%\setlength{\tabcolsep}{0pt}
%  \begin{tabular}{cc}
  \includegraphics[scale=0.9]{imaginet-omission-pos-boxplot.png}

  \includegraphics[scale=0.9]{imaginet-omission-dep-boxplot.png} 
%  \end{tabular}

\caption{Distribution of omission scores for POS (left) and dependency labels
  (right), for the {\sc Textual} and {\sc Visual} pathways and for
  {\sc LM}. Only labels which occur at least 1250 times are included.}
\label{fig:omission-imaginet}
\end{figure}

\begin{figure*}[t]
  \centering
  \hspace*{-0.2in}
  \setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.55]{imaginet-omission-ratio-pos-boxplot.png} &
  \includegraphics[scale=0.55]{imaginet-omission-ratio-dep-boxplot.png} \\  
  \end{tabular}
  \caption{Distributions of log ratios of omission scores of {\sc Textual} to {\sc Visual} per
    POS (left) and dependency labels (right). Only labels which occur at least 1250 times are included.}
\label{fig:omission-imaginet-ratio}
\end{figure*}

@@

Figure~\ref{fig:omission-imaginet-ratio} compares the two pathways of
{\sc Imaginet} directly using the log of the ratio of the {\sc Visual}
to {\sc Textual} omission scores, and plots the distribution of this
ratio for different POS and dependency labels.  Log ratios above zero
indicate stronger association with the {\sc Visual} pathway and below
zero with the {\sc Textual} pathway. We see that in relative terms,
{\sc Visual} is more sensitive to adjectives (JJ), nouns (NNS, NN),
numerals (CD) and participles (VBN), and {\sc Textual} to determiners
(DT), pronouns (PRP), prepositions (IN) as well finite verbs
(VBZ, VBP).

This picture is complemented by the analysis of the
relative importance of dependency relations: {\sc Visual} pays most
attention to the relations {\sc amod, nsubj, root,
  compound, dobj, nummod}
whereas {\sc Textual} is more sensitive to {\sc det, prep, aux, cc, poss, advmod, prt, relcl}.
As expected, {\sc Visual} is more focused on grammatical
functions typically filled by semantically contentful words, while
{\sc Textual} distributes its attention more uniformly and 
attends relatively more to purely grammatical functions.

@@

\begin{figure*}[t]
  \centering
  \hspace*{-0.2in}
  \setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.55]{imaginet-omission-quotient-pos-boxplot.png} &
  \includegraphics[scale=0.55]{imaginet-omission-quotient-dep-boxplot.png} \\  
  \end{tabular}
  \caption{Distributions of log ratios of omission scores of {\sc LM} to {\sc Textual} per
    POS (left) and dependency labels (right). Only labels which occur at least 1250times are included.}
\label{fig:omission-imaginet-quotient}
\end{figure*}
